Toward dynamic models of combat or lack thereof in animal mating

### 2016-01-11 ms.tex
tex formatting error
escalation probabilities

/* this is just for consideration I am not sure if it will be needed or useful */\\ \\
Number of mature males at time $t$:
\begin{equation} \label{eq:num_mature}
    K_{mature}(t) = \lfloor{K_{initial}(Pr({\rm mature} \, | m(t)) - S(t))}\rfloor
\end{equation}
A searching individual has a chance to encounter a nest equal to its ``exploration trait'' $\lambda_i$:
\begin{equation} \label{eq:encounter probability}
    Pr({\rm Encounter}) = \lambda_i
\end{equation}
The number of encounters that a searching individual has engaged in is:
\begin{equation} \label{eq:encounter rate}
    {\rm Encounters} = \lfloor\lambda_i \cdot t_{searching}\rfloor
\end{equation}
the average exploration trait across a cohort is $\bar\lambda$.

@@

\subsection{Contest Algorithm}
See Fig. \ref{fig:contests}.
For an occupier x' vs an invader x, there are 3 stages:
\begin{enumerate}
    \item Display 1
    \item Display 2
    \item Fight
\end{enumerate}
In the display phases the probability of escalation is dependant on the visible traits of x and x'
The rate of events increases as time t approaches t1

>>>>

/* this is just for consideration I am not sure if it will be needed or useful */\\
Number of mature males at time $t$:
\begin{equation} \label{eq:num_mature}
    K_{mature}(t) = \lfloor{K_{initial}(Pr({\rm mature} \, | m(t)) - S(t))}\rfloor
\end{equation}
A searching individual has a chance to encounter a nest equal to its ``exploration trait'' $\lambda_i$:
\begin{equation} \label{eq:encounter probability}
    Pr({\rm Encounter}) = \lambda_i
\end{equation}
The number of encounters that a searching individual has engaged in is:
\begin{equation} \label{eq:encounter rate}
    {\rm Encounters} = \lfloor\lambda_i \cdot t_{searching}\rfloor
\end{equation}
the average exploration trait across a cohort is $\bar\lambda$.

@@

\subsection{Contest Algorithm}
See Fig. \ref{fig:contests}.
For a defender $x_{def}$ vs an attacker $x_{atk}$, there are 3 stages:
each individual has an aggression trait $a$ and a mass $m$.\\
\begin{equation}\label{eq:logit}
    logit^{-1}(\alpha) = \frac{exp(\alpha)}{1 + exp(\alpha)}
\end{equation}

\begin{enumerate}
    \item Display 1
        Outcomes:
        \begin{itemize}
            \item $x_{atk}$ escalates: 
                $Pr(\rm{escalation}) =  logit^{-1}(a_{atk} \cdot m_{atk} - m_{def})$
                or leaves.
            \item $x_{def}$ escalates:
                $Pr(\rm{escalation}) =  logit^{-1}(a_{def} \cdot m_{def} - m_{atk})$ 
                or leaves.
            \item if the attacker leaves the defender keeps the nest
            \item if the defender leaves the attacker keeps the nest
            \item the attacker is evaluated first
            \item if they both escalate then the next stage occurs
        \end{itemize}
    \item Display 2:
        similar to stage 1, this could involve the $R$ value of the nest, or include the oponents aggression levels or energy reseves(?).
    \item Fight
\end{enumerate}
The cost of the fighting stage is much greater than the cost of the display stage.

In the display phases the probability of escalation is dependent on the visible traits of x and x'
The rate of events increases as time t approaches t1
